An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-14 VLDB2026/main.tex

		\setlength{\abovecaptionskip}{0.05cm}
		\setlength{\textfloatsep}{0.cm}
		\caption{Datassets}

		\label{tab:datasets_combined}
		\resizebox{\columnwidth}{!}{
			\begin{tabular}{cccccc}
				\toprule
				Dataset & Dimension & Base Data & Queries & LID & Type \\
				\midrule
				Msong & 420 & 992,272 & 200 & 23& Audio \\[2pt]
				Audio & 192 & 53,387 & 200 & 14& Audio \\[2pt]
				SIFT1M & 128 & 1,000,000 & 10,000 & 19& Image \\[2pt]
				GIST1M & 960 & 1,000,000 & 1,000 & 45& Image \\[2pt]
				GloVe & 100 & 1,183,514 & 10,000 & 47& Text \\[2pt]
				Enron & 1369 & 94,987 & 200 & 23& Text \\[2pt]
				Deep & 96 & 1,000,000 & 10,000 & 22& Image \\[2pt]
				YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\[2pt] 
				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\[2pt]

>>>>

		\setlength{\abovecaptionskip}{0.05cm}
		\setlength{\textfloatsep}{0.cm}
		\caption{Datasets}

		\label{tab:datasets_combined}
		\resizebox{\columnwidth}{!}{
			\begin{tabular}{cccccc}
				\toprule
				Dataset & Dimension & Base Data & Queries & LID & Type \\
				\midrule
				Msong & 420 & 992,272 & 200 & 23& Audio \\[2pt]
				Audio & 192 & 53,387 & 200 & 14& Audio \\[2pt]
				SIFT1M & 128 & 1,000,000 & 10,000 & 19& Image \\[2pt]
				GIST1M & 960 & 1,000,000 & 1,000 & 45& Image \\[2pt]
				GloVe & 100 & 1,183,514 & 10,000 & 47& Text \\[2pt]
				Enron & 1369 & 94,987 & 200 & 23& Text \\[2pt]
				Deep & 96 & 1,000,000 & 10,000 & 22& Image \\[2pt]
				YT-Audio& 128 & 1,000,000 & 10,000 & 15& Audio \\[2pt] 
				WIT & 2048 & 1,000,000 & 40,300 & 48& Image \\[2pt]
				Text2Image & 200 & 10,000,000 &10,000 & 59& Text2Image \\[2pt]
